---
title: "Week 3 Assignment notebook"
output: html_notebook
---
### Assignment Example
### The set() function made me very confused, since it has never been called in the whole process and seems not relevant with the question at all. Then I found this that very useful in explaining what happened: https://stackoverflow.com/questions/34811462/r-what-does-the-small-function-do-when-it-is-not-called-from-anywhere
```{r}
makeVector <- function(x = numeric()) {
        m <- NULL
        set <- function(y) {
                x <<- y
                m <<- NULL
        }
        get <- function() x
        setmean <- function(mean) m <<- mean
        getmean <- function() m
        list(set = set, get = get,
             setmean = setmean,
             getmean = getmean)
}

cachemean <- function(x, ...) {
        m <- x$getmean()
        if(!is.null(m)) {
                message("getting cached data")
                return(m)
        }
        data <- x$get()
        m <- mean(data, ...)
        x$setmean(m)
        m
}
```

```{r}
a <- c(2,4,6,8)
```

```{r}
b <- makeVector(a)
```

```{r}
print(b)
```

```{r}
b$get()
```

```{r}
b$set()
```

```{r}
b$setmean()
```
```{r}
b$getmean()
```
### run cachemean, since the mean was not calculated, the function will calculate the mean and store it in b

```{r}
cachemean(b)
```

### if you run cacheman again, you can find that the function detected the mean, and returned the message'getting cached data'

```{r}
cachemean(b)
```
### Concept of inverse matrix

```{r}
z <- matrix(c(2,9,6,5,3,8,6,4,7),3,3)
print(z)
```

```{r}
v <- solve(z)
print(v)
```
### you will get identity matrix if you multiply z and v, you will have to round it in R to get zeros.
```{r}
round(z %*% v)
```
### another example

```{r}
    A <- matrix( c(5, 1, 0,
                   3,-1, 2,
                   4, 0,-1), nrow=3, byrow=TRUE)
print(A)
```
```{r}
B <- solve(A)
print(B)
```
```{r}
C <- A %*% B
print(C)
```


